Gaudeamus 2017 Figures

### 2017-11-13 inst/examples/201705-Gaudeamus.Rmd
runs go through again

```{r init, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}
# Data files
input.data.file <- "df.combined.Gaudeamus2017.Rds"

>>>>

```{r init, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}
# Data files
#input.data.file <- "df.combined.Gaudeamus2017.Rds"
input.data.file <- "df.combined.20170125.Rds"
